ZCB Pricing

### 2018-07-04 ZCB Pricing .Rmd
in explicit: added comments and changed parameter values to match implicit

count <- 0 # set up count variable
for (i in rev(I)){ # rev is the reverse order of the time partition
  count <- count+1 # keeping track of loop
  for (j in (1+count):(nr-count)){
    pu <- sigma^2/(2*dr^2) + (alpha -beta*J[nr-j])/(2*dr) # up value
    pm <- 1/dt -sigma^2/(dr^2) # middle value
    pd <- sigma^2/(2*(dr^2)) - (alpha -beta*J[nr-j])/(2*dr) # down value
    V[j,i] <- (1/(J[nr-j]+1/dt))*(pu*V[j-1,i+1] + pm*V[j,i+1] +pd*V[j+1,i+1])
  }

@@

explicit(0.01,0.1,0.04,0.05,1:10)

>>>>

count <- 0 # set up count variable
for (i in rev(I)){ # rev is the reverse order of the time partition | i corresponds to the columns of the lattice
  count <- count+1 # keeping track of loop
  for (j in (1+count):(nr-count)){ # j corresponds to the rows of the lattice
    pu <- sigma^2/(2*dr^2) + (alpha -beta*J[nr-j])/(2*dr) # up value
    pm <- 1/dt -sigma^2/(dr^2) # middle value
    pd <- sigma^2/(2*(dr^2)) - (alpha -beta*J[nr-j])/(2*dr) # down value
    V[j,i] <- (1/(J[nr-j]+1/dt))*(pu*V[j-1,i+1] + pm*V[j,i+1] +pd*V[j+1,i+1])
  }

@@

explicit(0.08,0.8,0.005,0.05,1:10)
